Lab 5: Optimization: Answers

### 2023-02-15 Lab 5  Optim/Lab5_Optim.Rmd
Add files via upload

---
title: "Lab 5: Optimization"
author: "Eric Parajon"
output: pdf_document
---

@@

pacman::p_load(tidyverse,broom)
```

@@

Let's say we have a function $f(x)$ - we want to know what value of $x$ will maximize or minimize that function. In other words, let us say that the local maximum (or minimum) of a functtion is called $x^*$ (because it's the star on top of the plot of the function). Then we could say, for maximization, that:

@@

You would iterate Newton's method multiple times until it converges and finds the root. In theory, the algorithm would converge perfectly when we find that root - however, we'll never actually reach the root exactly. Why? (Think of Zeno's Paradox.) Thus, we need to either (or both) cap the number of interations or set some convergence criteria. For simplicity's sake, we'll just cap the maximum number of iterations here.

Here, we are going to set a starting point for the NR method of $\mu_0 = 10$. We will also set our iterations to 7, and then plot the score function with the values for each of these iterations. Don't worry so much about this code, but look at the plot. 
```{r, include = TRUE, message = FALSE, warning = FALSE}

@@

#Using `optim()` to maximize the log likelihood

@@

#just another way to simulate data
y <- rnorm(100, mean = X%*%theta_true[1:2], sd = theta_true[3])
```

>>>>

---
title: 'Lab 5: Optimization'
author: "Eric Parajon"
output:
  html_document:
    df_print: paged
---

@@

@@

Let's say we have a function $f(x)$ - we want to know what value of $x$ will maximize or minimize that function. In other words, let us say that the local maximum (or minimum) of a function is called $x^*$ (because it's the star on top of the plot of the function). Then we could say, for maximization, that:

@@

You would iterate Newton's method multiple times until it converges and finds the root. In theory, the algorithm would converge perfectly when we find that root - however, we'll never actually reach the root exactly. Why? (Think of Zeno's Paradox and asymptotes.) Thus, we need to either (or both) cap the number of iterations or set some convergence criteria. For simplicity's sake, we'll just cap the maximum number of iterations here.

Here, we are going to set a starting point for the NR method of $\mu_0 = 10$. We will also set our iterations to 7, and then plot the score function with the values for each of these iterations. Don't worry so much about this code, but look at the plot.

```{r, include=TRUE}
rm(list=ls())

#Installing and loading packages
pacman::p_load(tidyverse,broom)
```

```{r, include = TRUE, message = FALSE, warning = FALSE,fig.width=11, fig.height=5}

@@

# Using `optim()` to maximize the log likelihood

@@

#just another way to simulate data using matrix multiplication
y <- rnorm(100, mean = X%*%theta_true[1:2], sd = theta_true[3])
```

### 2023-02-15 Lab 5  Optim/Lab5_Optim_AnswerKey.Rmd
Add files via upload

---
title: "Lab 5: Optimization: Answers"
author: "Eric Parajon"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, include = FALSE)

@@

#Installing and loading packages for use
pacman::p_load(tidyverse,broom)
```

@@

You would iterate Newton's method multiple times until it converges and finds the root. In theory, the algorithm would converge perfectly when we find that root - however, we'll never actually reach the root exactly. Why? (Think of Zeno's Paradox.) Thus, we need to either (or both) cap the number of interations or set some convergence criteria. For simplicity's sake, we'll just cap the maximum number of iterations here.

@@

```{r, include = TRUE, message = FALSE, warning = FALSE}

>>>>

---
title: 'Lab 5: Optimization: Answers'
author: "Eric Parajon"
output:
  html_document:
    df_print: paged
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, include = FALSE)

@@

@@

You would iterate Newton's method multiple times until it converges and finds the root. In theory, the algorithm would converge perfectly when we find that root - however, we'll never actually reach the root exactly. Why? (Think of Zeno's Paradox and asymptotes.) Thus, we need to either (or both) cap the number of iterations or set some convergence criteria. For simplicity's sake, we'll just cap the maximum number of iterations here.

@@

```{r, include=TRUE}
rm(list=ls())

#Installing and loading packages
pacman::p_load(tidyverse,broom)
```

```{r, include = TRUE, message = FALSE, warning = FALSE,fig.width=11, fig.height=5}
